\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule\vspace{0.5em}]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}[\vspace{0.25em}]

\makeatletter
\renewcommand{\maketitle}{
    \begin{center}
        \vspace*{-1in}
        {\LARGE \bfseries \@title \par}
        \vspace{0.5em}
        {\large \@author \par}
        \vspace{1em}
        {\@date \par}
    \end{center}
    \vspace{1em}
}
\makeatother

\begin{document}

\title{\textbf{Seunghyeop Nam}}
\author{}
\date{}
\maketitle

\section*{Personal Information}
\textbf{Birth:} 10. Sep. 1999 \\
\textbf{Phone:} +82(0)-10-4017-4928 \\
\textbf{University Email:} \href{mailto:hyeobi@snu.ac.kr}{hyeobi@snu.ac.kr} \\
\textbf{Personal Email:} \href{mailto:hyeobi@hyeobi.com}{hyeobi@hyeobi.com} \\
\textbf{Web:} \href{https://www.hyeobi.com}{https://www.hyeobi.com}

\section*{Research Interests}
\textbf{Keywords:} Deep Reinforcement Learning (DRL), Robot Navigation (ROS2), Unknown Space Exploration, Fusion Learning, Cryptocurrency DRL Trading, Deep Learning \\
\textbf{Objective:} Advance the state of Deep Reinforcement Learning through innovative research in robot navigation, unknown space exploration, and fusion learning. Apply DRL techniques to interdisciplinary areas, including cryptocurrency trading, autonomous systems, and novel AI-driven applications.

\section*{Education}
\subsection*{\textbf{Konkuk University} \hfill Seoul, Korea}
Bachalor of Computer Science and Engineering \hfill \textit{Mar. 2019 – Aug. 2025}

\section*{Publications}
\textbf{Seunghyeop Nam}, Changseok Woo, Sinkyu Kang, Tuan Anh Nguyen, and Dugki Min. "iNAV-drlSLAM: An Improved Indoor Self-Driving Framework for Mobile Robots using Deep Reinforcement Learning integrated with SLAM." In 2023 15th International Conference on Advanced Computational Intelligence (ICACI), pp. 1-8. IEEE, 2023. \\ \\
\textbf{Seunghyeop Nam}, Changseok Woo, Sinkyu Kang, Tuan Anh Nguyen, and Dugki Min. "SLAM-DRLnav: A SLAM-Enhanced Deep Reinforcement Learning Navigation Framework for Indoor Self-driving." In 2023 International Conference on Mechatronics, Control and Robotics (ICMCR), pp. 44-48. IEEE, 2023. \\ \\
\textbf{Seunghyeop Nam}, Tuan Anh Nguyen, Eunmi Choi, and Dugki Min. "FH-DRL: Exponential-Hyperbolic Frontier Heuristics with DRL for accelerated Exploration in Unknown Environments." 2025 IEEE Transactions on Intelligent Vehicles [Under Review]. \\ \\
\textbf{Seunghyeop Nam}, Tuan Anh Nguyen, Eunmi Choi, and Dugki Min. "A Multi-head Fusion-based Actor-Critic Deep Reinforcement Learning with Memory Contextualise for End-to-End Autonomous Navigation" 2024 IEEE Transactions on Intelligent Vehicles [Under Review]. \\ \\
\textbf{Seunghyeop Nam}, Tuan Anh Nguyen, Eunmi Choi, and Dugki Min. "FH-DRL: Exponential-Hyperbolic Frontier Heuristics with DRL for accelerated Exploration in Unknown Environments." 2025 IEEE Transactions on Intelligent Vehicles [Under Review]. \\ \\
Tuan Anh Nguyen, Damsub Lim, \textbf{Seunghyeop Nam}, Dugki Min, Eunmi Choi, Iure Fe, Franciso Airton Silva and Paulo Maciel. "Metaverse Edge Computing: On Aging Dependability Analysis of Edge-in-the-loop Simulation Platform for AAM Vehicle Digital Twin" MetaCom 2025 [Under Review]. \\ \\
\textbf{Seunghyeop Nam}, Seunghyeon Kang, Tuan Anh Nguyen, Eunmi Choi and Dugki Min. "PGELU: Metaverse-Driven Deep Learning Boosted by A Parametric GELU for Stable and Scalable Recognition of Emotions and 3D Objects" MetaCom 2025 [Under Review]. \\ \\



\section*{Research Experience}
\subsection*{\textbf{Konkuk University, Distributed Multimedia Systems (DMS) Lab} \hfill Seoul, Korea}
\textit{Undergraduate Researcher} \hfill \textit{Jul. 2021 – Present}
\begin{itemize}
	\item Participated in the Midcareer Researcher Grant, Participating Intelligent MAEC Collaborative Framework (i-MeC2 Framework)
    \item Conducted research on robot navigation technologies, including Simultaneous Localization and Mapping (SLAM), sensor fusion, stabilization, and frontier-based exploration using Deep Reinforcement Learning.
    \item Developed state-of-the-art DRL algorithms for applications in cryptocurrency trading and robotic systems.
    \item Designed neural networks for disease detection in both human and agricultural contexts.
\end{itemize}


\section*{Projects}
\subsection*{\textbf{LG ThinQ} \hfill Seoul, Korea}
\textit{Primary Developer for Industrial Project: "Smart Mirror"} \hfill \textit{Feb. 2021 – Dec. 2021}
\begin{itemize}
    \item Developed a Smart Mirror system capable of displaying dynamic information such as weather forecasts, news headlines, and calendars.
    \item Integrated natural language processing (NLP) capabilities for conversational interactions with users.
    \item Implemented emotion detection and classification algorithms to recommend attire based on users' current mood.
\end{itemize}

\subsection*{\textbf{Dream Semeter} \hfill Seoul, Korea}
\textit{Quant trading of Cryptocurrency using DRL} \hfill \textit{Aug. 2024 – Dec. 2024}
\begin{itemize}
    \item Developed and implemented a deep reinforcement learning (DRL)-based crypto trading strategy to optimize portfolio returns.
    \item Designed and trained DRL models using advanced reinforcement learning algorithms such as DDPG, TD3, and SAC.
    \item Built a backtesting framework to evaluate strategy performance against historical cryptocurrency market data.
\end{itemize}

\section*{Awards and Honors}
\begin{itemize}
    \item 1st Place, VEX Robotics National Competition \hfill \textit{2017}
    \item Participant and Judge, VEX Robotics World Championship \hfill \textit{2017}
\end{itemize}

\section*{Additional Information}
\textbf{Programming Skills}: Python, C, C++, ROS2, Java, Javascript, Kotlin, MATLAB, SQL, Computer Vision, Deep Learning, Deep Reinforcement Learning. \\
\textbf{Languages}: Korean (native fluency), English (professional proficiency), German (A2) \\
\textbf{Military Service}: Alternative military service as a Social Service Agent in the Republic of Korea (Oct. 2023 – Jul. 2025). \\
\textbf{Certificate and Licences}:
\begin{itemize}
	\item Driver's Licence (Republic Of Korea): 1st Class (Ordinary) \hfill \textit{Dec. 2017}
	\item Driver's Licence (Republic Of Korea): 2nd Class (Small) \hfill \textit{Aug. 2018}
	\item Craftsman Bartender (Human Resources Development Service of Korea) \hfill \textit{Apr. 2019}
	\item MOS PowerPoint(Microsoft) \hfill \textit{Apr. 2019}
	\item MOS Excel Core(Microsoft) \hfill \textit{Jun. 2019}
\end{itemize}

\end{document}
